\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{ragged2e}
\usepackage{etoolbox}
\usepackage{tikz}
\input{glyphtounicode}

% font options
\usepackage{newpxtext}
\linespread{1.05}  % palladio needs more leading (space between lines)
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{}  % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\footskip}{5pt}

% sections formatting
\titleformat{\section}{
  \vspace{-2pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

% ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

% custom commands
\newcommand{\cvitem}[1]{
  \item\small{
    {#1\vspace{-2pt}}
  }
}

\newcommand{\cvheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \small#3 & \small #4 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\cvheadingstart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\cvheadingend}{\end{itemize}}
\newcommand{\cvitemstart}{\begin{itemize}\justifying}
\newcommand{\cvitemend}{\end{itemize}\vspace{-5pt}}

\newcommand{\cvskill}[2]{
  \textcolor{black}{\textbf{#1}}\hfill
  \foreach \x in {1,...,5}{%
    \space{\ifnumgreater{\x}{#2}{\color{black!80!white!20}}{\color{black}}\faSquare}}\par%
  \vspace{-2pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\footnotesize$\bullet$}}$}

\begin{document}
\begin{center}
  \textbf{\LARGE\scshape Desmond Mehta} \\
  \vspace{1pt}\small
  \href{mailto:desmond.mehta@yale.edu}{desmond.mehta@yale.edu}
  $\ \diamond\ $
  New Haven, CT
  $\ \diamond\ $
  \href{https://github.com/dezash123}{https://github.com/dezash123}
\end{center}


\section{Education}
\cvheadingstart
  \cvheading
    {Yale University}{New Haven, CT}
    {B.S. + M.S. in Computer Science}{2024 -- 2028}
  \cvheading
    {Cold Spring Harbor High School}{Cold Spring Harbor, NY}
    {4.22 GPA, 1580 SAT}{2020 -- 2024}
  \cvitemstart
    \cvitem{Relevant coursework: Linear Algebra, Multivariable Calculus, Physics C (Mechanics and E\&M), 12x AP's with 5's}
  \cvitemend
  \cvheading
    {Columbia University Science Honors Program}{New York, NY}{Weekend classes in Relativity, Quantum Computing, and Materials Science.}{2022 -- 2024}
\cvheadingend


\section{Research}
\cvheadingstart

  \cvheading
    {Asynchronous VLSI and Architecture Group}{Yale University}
    {Undergraduate Researcher}{January 2025 -- Present}
  \cvitemstart
    \cvitem{Designing silicon modules for inter-chip communication.}
  \cvitemend
  
  \cvheading
    {Bioelectronics Lab}{Feinstein Institutes for Medical Research}
    {Research Intern}{Summer 2024}
  \cvitemstart
    \cvitem{Improved custom radio transmission protocol for rodent-implanted neural recording device.}
  \cvitemend
  
  \cvheading
    {Neural Acoustic Processing Lab}{Columbia Engineering}
    {Research Intern}{Summer 2023}
  \cvitemstart
    \cvitem{Worked with MATLAB signal processing to develop methods for minimally-invasive neural implants.}
  \cvitemend

  \cvheading
    {Human Brain Mapping Lab}{Feinstein Institutes for Medical Research}
    {Research Intern}{Summer 2022 -- March 2023}
  \cvitemstart
    \cvitem{Worked with Python signal processing to study the role of Sharp Wave-Ripples in memory.}
  \cvitemend
  
\cvheadingend


\section{Activities}
\cvheadingstart
  \cvheading
    {Yale Undergraduate Aerospace Association}{New Haven, CT}
    {CubeSat Architecture and Security Board Lead and Project Liquid Team Member}{Fall 2024 -- Present}
  \cvitemstart
    \cvitem{Migrating satellite codebase from C to C++ and planning of higher-level design paradigms.}
    \cvitem{Designing new STM32-based motherboard for liquid-fuel rocket; rewriting codebase in Rust.}
  \cvitemend

  \cvheading
    {FIRST Robotics Competition}{Cold Spring Harbor, NY}
    {Build Captain, CAD Captain, Field Technician}{2021-2024}
  \cvitemstart
    \cvitem{Qualified for World Championship in 2023 and 2024.}
    \cvitem{2024: Developed autonomous targeting system in addition to leading design.}
  \cvitemend

  \cvheading
    {Lemelson-MIT InvenTeam}{Cambridge, Massachusetts}{Team Founder and Technical Lead; 1 of 8 teams nationally selected to receive \$7500 grant.}{Summer 2023 -- Spring 2024}

\cvheadingend

\section{Experience/Personal Projects}
\cvheadingstart
  \cvitem{Mechatronics: Designed 2 robots for NHRL Combat Robotics Competition; designed motherboard for custom FPV drone}
  \cvitem{Embedded Systems:  Programmed drone in Rust including drivers and control systems; currently developing a smartwatch}
  \cvitem{Programming: Experienced in C, Rust, C++, Python, MATLAB, Java, Javascript, Kotlin, Verilog, CUDA}
  \cvitem{CAD: Experienced in Onshape, Solidworks, Fusion360,  KiCad, Magic VLSI}
  \cvitem{2024 Congressional App Challenge Winner, District NY01}
\cvheadingend


\end{document}
